Quality control for the target decoy approach for peptide identification

### 2022-11-13 index.Rmd
update theme index.html

---
title: Quality control for the target decoy approach for peptide identification
output:
    html_document:
      code_download: false
      toc: false
      toc_float: false
      number_sections: false

---

>>>>

---
title: Quality control for the target decoy approach for peptide identification
output:
    html_document:
      code_download: false
      toc: false
      toc_float: false
      number_sections: false
      theme: flatly
      highlight: tango
---
